---
title: "Writing functions"
author: "Amin Yakubu"
date: "10/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rvest)
```

```{r}
x = rnorm(25, mean = 5, sd = 3)

(x - mean(x)) / sd(x)
```

Write a function to compute z scores for a vector

```{r}
z_scores = function(x){
  
  (x - mean(x)) / sd(x)
}
```

Check to see if it works...

```{r}
y = runif(100)

z_scores(y)

## Same as above 
unif_sample = runif(100)

z_scores(x = unif_sample)
```


Check some other examples 

```{r, error = TRUE}

z_scores(3)

z_scores("my name is amin")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

Put in some checks on inputs...


```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  (x - mean(x)) / sd(x)

}
```

```{r, error = TRUE}

z_scores(3)

z_scores("my name is amin")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```


### mean and sd

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
 mean_x = mean(x)
 sd_x = sd(x)
 
 c(mean_x, sd_x)

}

mean_and_sd(unif_sample)
```

Putting the resutls in a tibble instead

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
tibble(
 mean_x = mean(x),
 sd_x = sd(x)
 )

}

mean_and_sd(unif_sample)
```

## Multiple inputs

Look at simple linear regression!

```{r}
sim_data = tibble(
  x = rnorm(30, 1, 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)

beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

Write a function that simulates data, fits the model, and returns the estimates. Inputs are sample size and true coefficients.

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

```{r}
sim_regression(n = 30, beta0 = 0, beta1 = -1)

sim_regression(n = 300)
```

Scrapping Amazon

```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

We can use functions if we wanted multiple pages

```{r, eval = FALSE}

extract_reviews = function(url){
dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
  reviews
}

```








